---
title: "Appendix: Kyle & Eguchi (2021)"
author: "Kristopher Kyle & Masaki Eguchi"
output: 
  html_document:
    df_print: paged
    toc: true
    number_sections: true
    toc_depth: 4
    toc_float:  
      collapsed: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(MuMIn)
library("relaimpo")
library(sjPlot)
library(tidyverse)
library(car)
library(gridExtra)
library(psych)
library(table1)

a <- read.csv("granger_output_2019-11-19.csv")

#this does grand mean centering
center_colmeans <- function(x) {
    xcenter = colMeans(x)
    x - rep(xcenter, rep.int(nrow(x), ncol(x)))
}

pred_plot <- function(x1, y1, dat) {
  ggplot(dat, aes(x = x1,y = y1)) +
    geom_smooth(method = "lm") +
    labs(x = colname(dat$x1), y = colname(dat$y1))
}

a2 <- read.csv("5_mc_refined_dataset.csv")
a2$filename<-NULL #delete filenames
a2$nwords <- NULL #delete nwords
a2$X <- NULL #delete empty column (from pandas)

a3 <- as.data.frame(cbind(a2[,1], center_colmeans(a2[,2:12])))
names(a3)[1]<-paste("Score")
attach(a3)
```



# Descriptive stats

```{r}
describe(a3)
```


## Dependent variable
```{r }
hist(a$Score)
```

```{r }
hist(a$nwords)
```

## Independent variable
```{r }
hist(a$b_concreteness)
```


```{r }
hist(a$mcd)
```

```{r}
hist(a$usf)

```


```{r }
cor.test(a$Score,a$b_concreteness)
```


```{r }
cor.test(a$Score,a$mcd)
```


```{r }
cor.test(a$Score,a$usf)
```


### nsubjects
```{r}
hist(a$v_nsubj_deltap_govcue)
```


```{r}
hist(a$v_nsubj_deltap_depcue)
```


```{r}
hist(a$v_nsubj_deltap_strgst)
```

```{r}
hist(a$v_nsubj_MI)
```


```{r}
hist(a$v_nsubj_T)
```

### Dobj histograms
```{r}
hist(a$v_dobj_deltap_govcue) #heavily skewed (right tail)
```


```{r}
hist(a$v_dobj_deltap_depcue)
```


```{r}
hist(a$v_dobj_deltap_strgst) #looks the nicest
```


```{r}
hist(a$v_dobj_MI)
```


```{r}
hist(a$v_dobj_T)
```

### Adv mod
```{r}
hist(a$v_advmod_deltap_govcue)
```


```{r}
hist(a$v_advmod_deltap_depcue)
```




```{r}
hist(a$v_advmod_deltap_strgst)
```




```{r}
hist(a$v_advmod_MI)
```




```{r}
hist(a$v_advmod_T)
```


### Amod
```{r}
hist(a$n_amod_deltap_govcue,breaks = 50) # some outliers
```


```{r}
hist(a$n_amod_deltap_depcue,breaks = 50)
```




```{r}
hist(a$n_amod_deltap_strgst,breaks = 50)
```

```{r}
hist(a$n_amod_MI,breaks = 50)
```


```{r}
hist(a$n_amod_T,breaks = 50)
```


## Picking the variable based on the normally distributed indices
refined normal indices using python script...


```{r}
varnames <- rbind("McD CD", "USF CD", "Verb—Nsubject DeltaP Dep", "Verb—Dobj (MI)", "Verb—Advmod Delta P Strongest", "Noun—Amod (MI)", "Adjective Frequency (Logged)", "Adverb Frequency (Logged)", "Main verb Frequency (Logged)", "Content word lemma Frequency", "Lemma bigram DeltaP Strongest")

IndexCategory <- rbind("Contextual distinctiveness", "Contextual distinctiveness", "Dependency bigram", "Dependency bigram", "Dependency bigram", "Dependency bigram", "Word Frequency", "Word Frequency", "Word Frequency", "Word Frequency", "Bigram")

```


```{r}
#desc <- describe(a2[,2:12])
#desc$variable <- varnames
#write.csv(desc, "descriptives.csv")
```

```{r}
#corr <- as.data.frame(cor(a2[,2:12]))
##corr$variable <- varnames
#write.csv(corr, "correlations.csv")
```

# Correlation with the dependent variable
```{r}
correlation <- corr.test(y = a2$Score, x = a2[,2:12], method = "pearson")

cor_result2 <- as.data.frame(cbind(varnames, IndexCategory,correlation$r, correlation$se))

cor_result <- cbind(varnames, IndexCategory,print(correlation, short = F, digit = 3))
cor_result$cor_abs <- abs(cor_result$raw.r)
```


```{r correlation plots}
ggplot(cor_result, aes(x = reorder(varnames, cor_abs), y = raw.r, family = "serif", fill = IndexCategory, shape = IndexCategory), ymax = .5, ymin = -.5)+
  geom_bar( stat = "identity", width = .7) +
  geom_pointrange(aes(x = reorder(varnames, cor_abs), y =  raw.r, ymin = raw.lower, ymax = raw.upper, width = .15)) + 
  ylim(-1, 1) +
  geom_text(aes(y = -.79, label = raw.r, size = 1.7), hjust = "outward", family = "serif") +
  coord_flip() +
  theme_bw()+
  labs(x = "Lexical and phraseological indices", y = "Pearson Correlation Coefficients") +
  theme(legend.position="bottom") +
  scale_size(guide = 'none')

```


# Regression modeling 

## Constructing a full model
```{r Regression with }
#create model, use dredge for all subsets.
full_mod <- lm(Score ~ .,data = a3)
summary(full_mod)

options(na.action = "na.fail")
drge <- dredge(full_mod)
```


## Model selection through best-subset regression
```{r}
sel_models_aic <- model.sel(drge)
sel_models_aic[1:10]
```

## Model selection using BIC
```{r}
sel_models_bic <- model.sel(drge, rank = BIC)

sel_models_bic[1:10]
```



```{r}
best_mod_aic <- lm(Score ~ adv_manner_freq_log+amod_freq_log+cw_lemma_freq_log + a2$lex_mverb_freq_log +mcd + n_amod_MI+ usf + v_advmod_deltap_strgst+v_dobj_MI, data = a3)
summary(best_mod_aic)
```


## Best regression model 1
- supression for the lexical frequency
- removed from the model 
```{r}
best_mod_bic <- lm(Score ~ lex_mverb_freq_log +mcd + n_amod_MI+ usf + v_advmod_deltap_strgst+v_dobj_MI, data = a3)
summary(best_mod_bic)
```

## Best regression model 2

```{r}
best_mod_bic2 <- lm(Score ~ mcd + n_amod_MI+ usf + v_advmod_deltap_strgst+v_dobj_MI, data = a3)
summary(best_mod_bic2)
```


```{r}
BIC(best_mod_bic2)
```


## Final model information in a table format
```{r}
tab_model(best_mod_bic2, show.std = T, show.se = T, show.aic = T, col.order = c("est", "se",  "p", "std.est", "std.ci", "ci.inner", "ci.outer", "stat", "df",
  "response.level"), digits = 3)

```

## Calculating importance
```{r}
calc.relimp(best_mod_bic2)
```


## Marginal effects plot
```{r}
plot_model(best_mod_bic2, type = 'pred')
```


## Checking the assumption

### residual plots
```{r}
plot(best_mod_bic2)
```

### Collinearity diagnosis
```{r}
1/vif(best_mod_bic2)

```




